InteroceptionScale - Data Analysis

### 2024-12-11 study1/analysis/2_analysis.qmd
Cleaning script updates
analysis

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(EGAnet)
library(tidygraph)
library(ggraph)
```

@@

df <- read.csv("../data/rawdata_participants.csv")

@@

```{r}
bootstrap_similarity <- function(df) {
  rez <- data.frame()
  for(i in 1:200) {
    idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
    newdata <- df[idx,]
    items <- select(df, contains("_Q"))
    byfacet <- items[newdata$Condition=="Dimensions",]
    bymodality <- items[newdata$Condition=="Domains",]
    byrandom <- items[newdata$Condition=="Random",]

@@

rez <- bootstrap_similarity(df)

rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(name %in% c("PSI", "RV", "RVadj", "SMI")) |>
  mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |>
  ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
  ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
  facet_wrap(~Sample) +
  scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
  scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
  labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
  theme_minimal()
```

@@

p_sim <- rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |>
  filter(Sample == "Random") |> 
  ggplot(aes(x=value, y=name)) +
  ggdist::stat_eye(aes(fill = after_stat(x < 0))) +
  geom_vline(xintercept=0, linetype="dashed") +
  labs(x="Similarity Difference", y="Indices of pattern difference",
       title="To which matrix is the random one more similar?",
       fill="More similar to") +
  theme_minimal() +
  scale_fill_manual(values=c("TRUE"="#F44336", "FALSE"="#2196F3"), labels = c("By modality", "By facet"))

@@

make_corplot <- function(data, order) {
  rownames_to_column(as.data.frame(cor(data)), "item") |> 
    pivot_longer(-item) |> 
    mutate(item = fct_relevel(item, order),
           name = fct_relevel(name, order)) |>
    ggplot(aes(x=name, y=item, fill=value)) +
    geom_tile() +
    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
    theme_minimal() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          legend.position = "none")
}

@@

p1 / (p2 | p_sim | p3) + patchwork::plot_layout(heights=c(3, 1)) + patchwork::plot_annotation(title="Effect of Item-presentation Grouping", theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
```

@@

uva <- EGAnet::UVA(items, cut.off = 0.2)

correlation::correlation(items[unlist(uva$redundant)],
                         items[names(uva$redundant)]) |>
  mutate(Parameter1 = fct_relevel(Parameter1, unlist(uva$redundant)),
         Parameter2 = fct_relevel(Parameter2, names(uva$redundant))) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=insight::format_value(r)), color="white") +
  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x="Removed Items", y="Kept Items", fill="Correlation")

toremove1 <- uva$keep_remove$remove
```

@@

ega1 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

```{r}
#| fig-width: 10
#| fig-height: 12

@@

toremove2 <- filter(itemstability_table, Max < 0.8)$Item

itemstability_table |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("white", "orange", "green"),
                 domain = c(0, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove2, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Stability**"),
    subtitle = "Proportion of times an item is assigned to the same cluster"
  ) |>
  gt::fmt_number(columns=-Item, decimals=3)
```

@@

ega2 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

plot(itemStability(ega2, IS.plot=FALSE))
```

```{r}
lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)

@@

ega3 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=TRUE,
  iter=500,
  seed=3, ncores = 4)

@@

```{r}
load("models/ega3.RData")

# itemStability(ega2)

@@

higher$Item <- paste0("H", higher$Item)
higher$Label <- paste("TODO", 1:nrow(higher))
lower <- mutate(lower, Label = labels[Item], Item = 1:n())

rbind(higher, lower) |>
  datawizard::data_relocate("Label", after = "Item") |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::tab_row_group(
    label = "Item",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Higher Order",
    rows = 1:nrow(higher)
  ) |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::tab_style(
    style = gt::cell_text(size="small", style="italic"),
    locations = gt::cells_body(columns="Label")
  ) |>
  gt::tab_style(
    style = list(gt::cell_text(weight="bold"),
                 gt::cell_fill(color = "#F5F5F5")),
    locations = list(
      gt::cells_row_groups(groups = "Item"),
      gt::cells_row_groups(groups = "Higher Order")
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFCDD2"),
    locations = list(
      gt::cells_column_labels(columns = 3),
      gt::cells_body(columns="Item", rows=c(1, 6:8))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFCCBC"),
    locations = list(
      gt::cells_column_labels(columns = 4),
      gt::cells_body(columns="Item", rows=c(9:11))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFE0B2"),
    locations = list(
      gt::cells_column_labels(columns = 5),
      gt::cells_body(columns="Item", rows=c(12:14))
    )
  ) |>
  gt::fmt_number(columns=-Item, decimals=2) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  )
```

@@

```{r}
graph <- convert2tidygraph(ega3)

tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |>
  ggraph::ggraph(layout = 'mds') +
  ggraph::geom_edge_arc(aes(edge_alpha=as.numeric(type == "virtual")), edge_width=0.2, strength=0, color="grey") +
  ggraph::geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real")), strength=0.1) +
  ggraph::geom_node_point(aes(color=dimension, shape=level), size=10, alpha=0.7) +
  ggraph::geom_node_text(aes(label=name), repel=TRUE) +
  scale_edge_alpha(range = c(0, 0.9), guide="none") +
  scale_edge_width(range = c(0.2, 3), guide="none") +
  scale_shape_manual(values=c("Higher"="square", "Lower"="circle")) +
  theme_void()
```

<!-- ::: {.panel-tabset} -->

<!-- ### Full Sample -->

<!-- ### By Dimension / Domains / Context -->

<!-- ```{r} -->
<!-- bydimension <- items[df$Condition=="Dimensions",] -->

<!-- ega_bydimension <- EGA(bydimension[, 1:20], plot.EGA = FALSE) -->

<!-- plot(ega_bydimension) -->
<!-- ``` -->

<!-- ### By Modalities -->

<!-- ```{r} -->
<!-- bymodality <- items[df$Condition=="Domains",] -->

<!-- ega_bymodality <- EGA(bymodality[, 1:20], plot.EGA = FALSE) -->

<!-- plot(ega_bymodality) -->
<!-- ``` -->

<!-- ::: -->

<!-- ## Model Comparison -->

<!-- ```{r} -->
<!-- # EGAnet::EGM(items[, 1:60]) -->

<!-- # EGAnet::EGM.compare(items[, 1:20]) -->

<!-- # rez <- EGAnet::network.compare(byfacet, bymodality, seed=3) -->
<!-- # plot(rez) -->
<!-- ``` -->

@@

```{r}
# Modelbased scores
scores <- EGAnet::net.scores(
  items[names(ega3$typicalGraph$lower_order$wc)],
  A=ega3$typicalGraph$lower_order$graph,
  wc=ega3$typicalGraph$lower_order$wc)$scores$std.scores |>
  as.data.frame()
names(scores) <- paste0("C", names(scores))

>>>>

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(EGAnet)
library(tidygraph)
library(ggraph)

set.seed(42)
```

@@

df <- read.csv("../data/data_participants.csv")

@@

```{r}
#| eval: true

bootstrap_similarity <- function(df) {
  rez <- data.frame()
  for(i in 1:200) {
    idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
    newdata <- df[idx,]
    items <- select(df, contains("_Q"))
    byfacet <- items[newdata$Condition=="Dimensions",]
    bymodality <- items[newdata$Condition=="Domains",]
    byrandom <- items[newdata$Condition=="Random",]

@@

rez <- bootstrap_similarity(df)
```

@@

rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(name %in% c("PSI", "RVadj", "SMI")) |>
  mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |>
  ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
  ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
  facet_wrap(~Sample) +
  scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
  scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
  labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
  theme_minimal()
```

```{r}
#| fig-width: 10
#| fig-height: 10
#| eval: true

p_sim <- rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |>
  filter(Sample == "Random") |> 
  ggplot(aes(x=value, y=name)) +
  ggdist::stat_eye(aes(fill = after_stat(x < 0))) +
  geom_vline(xintercept=0, linetype="dashed") +
  labs(x="Similarity Difference", y="Indices of pattern difference",
       title="To which matrix is the random one more similar?",
       fill="More similar to") +
  theme_minimal() +
  scale_fill_manual(values=c("TRUE"="#2196F3", "FALSE"="#4CAF50"), labels = c("By modality", "By facet"))

@@

make_corplot <- function(data, order) {
  rownames_to_column(as.data.frame(cor(data)), "item") |> 
    pivot_longer(-item) |> 
    mutate(item = fct_relevel(item, order),
           name = fct_relevel(name, order)) |>
    ggplot(aes(x=name, y=item, fill=value)) +
    geom_tile() +
    # scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, values=c(-1, 0, 1)) +
    scale_fill_gradientn(
      colors=c("blue", "white", "#FFEE58", "#FFC107", "#FF9800", "#FF5722", 
               "#F44336", "#E91E63", "#9C27B0", "#8231B4", "#673AB7", "white"), 
      values=c(-1, seq(0, 1, 0.1))) +
    theme_minimal() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          legend.position = "none")
}

@@

p1 / (p2 | p_sim | p3) + 
  patchwork::plot_layout(heights=c(3, 1)) + 
  patchwork::plot_annotation(
    title="Effect of Item-presentation Grouping", 
    theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
```

@@

uva <- EGAnet::UVA(items, cut.off = 0.25, reduce.method="remove", verbose=FALSE)

toremove1 <- unique(uva$keep_remove$remove)
keep <- uva$keep_remove$keep[!uva$keep_remove$keep %in% toremove1]

sorted <- correlation::cor_sort(cor(items[toremove1],items[keep]))

correlation::correlation(items[toremove1], items[keep]) |>
  mutate(Parameter1 = fct_relevel(Parameter1, rownames(sorted)),
         Parameter2 = fct_relevel(Parameter2, colnames(sorted))) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=insight::format_value(r)), color="white") +
  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, guide="none") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x="Removed Items", y="Kept Items", fill="Correlation")
```

@@

ega1 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

```{r}
#| fig-width: 12
#| fig-height: 14
#| fig-keep: "first"

@@

# Remove items
toremove2 <- filter(itemstability_table, Max < 0.8)$Item
toremove2 <- itemstability_table |> 
  filter(!Item %in% toremove2) |>
  mutate(Item, n=n(), .by="Cluster", .keep="used") |> 
  filter(n < 3) |>  # Remove small clusters
  pull(Item) |> 
  c(toremove2)
```

```{r}
#| fig-width: 12
#| fig-height: 14
#| fig-keep: "first"

# plot(itemstability)
```

```{r}
itemstability_table |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("white", "orange", "green"),
                 domain = c(0, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove2, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Stability**"),
    subtitle = "Proportion of times an item is assigned to the same cluster"
  ) |>
  gt::fmt_number(columns=-Item, decimals=3)
```

@@

ega2 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

plot(itemStability(ega2, IS.plot=FALSE))

# itemstability_table <- make_loadingtable(itemstability$lower_order$item.stability$all.dimensions)
# toremove2 <- filter(itemstability_table, Max < 0.7)$Item
```

```{r}
#| message: false

lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)

@@

ega3 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=TRUE,
  iter=500,
  seed=3, ncores = 4)

@@

```{r}
#| fig-width: 12
#| fig-height: 14
#| fig-keep: "first"

load("models/ega3.RData")

plot(itemStability(ega3))
```

```{r}
#| message: false

@@

higher$Item <- paste0("H", higher$Item)
higher$Label <- paste("TODO", 1:nrow(higher))
lower <- mutate(lower, Label = labels[Item], ID= Item, Item = 1:n())

rbind(higher, select(lower, -ID)) |>
  datawizard::data_relocate("Label", after = "Item") |>
  select(-Cluster, -Max) |>
  # datawizard::data_rename(c(XC1 = "C01", XC2 = "C02")) |> 
  gt::gt() |>
  gt::tab_row_group(
    label = "Items",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Metaclusters",
    rows = 1:nrow(higher)
  ) |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::tab_style(
    style = gt::cell_text(size="small", style="italic"),
    locations = gt::cells_body(columns="Label")
  ) |>
  gt::tab_style(
    style = list(gt::cell_text(weight="bold"),
                 gt::cell_fill(color = "#F5F5F5")),
    locations = list(
      gt::cells_row_groups(groups = "Items"),
      gt::cells_row_groups(groups = "Metaclusters")
  ) |>
  # Metacluster 1
  gt::tab_style(
    style = gt::cell_fill(color = "#B39DDB"),
    locations = list(
      gt::cells_column_labels(columns = 3),
      gt::cells_body(columns="Item", rows=c(4:6))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#9FA8DA"),
    locations = list(
      gt::cells_column_labels(columns = 4),
      gt::cells_body(columns="Item", rows=c(7:9))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#90CAF9"),
    locations = list(
      gt::cells_column_labels(columns = 5),
      gt::cells_body(columns="Item", rows=c(1, 10:12))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#81D4FA"),
    locations = list(
      gt::cells_column_labels(columns = 6),
      gt::cells_body(columns="Item", rows=c(13:15))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#80DEEA"),
    locations = list(
      gt::cells_column_labels(columns = 7),
      gt::cells_body(columns="Item", rows=c(16:18))
  ) |>
  # Metacluster 2
  gt::tab_style(
    style = gt::cell_fill(color = "#F3F29D"),
    locations = list(
      gt::cells_column_labels(columns = 8),
      gt::cells_body(columns="Item", rows=c(19:21))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#E6EE9C"),
    locations = list(
      gt::cells_column_labels(columns = 9),
      gt::cells_body(columns="Item", rows=c(22:24))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#D6E8A1"),
    locations = list(
      gt::cells_column_labels(columns = 10),
      gt::cells_body(columns="Item", rows=c(25:27))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#C5E1A5"),
    locations = list(
      gt::cells_column_labels(columns = 11),
      gt::cells_body(columns="Item", rows=c(2, 28:30))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#B5DCA6"),
    locations = list(
      gt::cells_column_labels(columns = 12),
      gt::cells_body(columns="Item", rows=c(31:33))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#A5D6A7"),
    locations = list(
      gt::cells_column_labels(columns = 13),
      gt::cells_body(columns="Item", rows=c(34:36))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#93D1B6"),
    locations = list(
      gt::cells_column_labels(columns = 14),
      gt::cells_body(columns="Item", rows=c(37:39))
  ) |>
  # Metacluster 3
  gt::tab_style(
    style = gt::cell_fill(color = "#CE93D8"),
    locations = list(
      gt::cells_column_labels(columns = 15),
      gt::cells_body(columns="Item", rows=c(40:42))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#F48FB1"),
    locations = list(
      gt::cells_column_labels(columns = 16),
      gt::cells_body(columns="Item", rows=c(43:45))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#EF9A9A"),
    locations = list(
      gt::cells_column_labels(columns = 17),
      gt::cells_body(columns="Item", rows=c(3, 46:48))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFAB91"),
    locations = list(
      gt::cells_column_labels(columns = 18),
      gt::cells_body(columns="Item", rows=c(49:51))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFCC80"),
    locations = list(
      gt::cells_column_labels(columns = 19),
      gt::cells_body(columns="Item", rows=c(52:54))
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFE082"),
    locations = list(
      gt::cells_column_labels(columns = 20),
      gt::cells_body(columns="Item", rows=c(55:57))
  ) |>
  gt::fmt_number(columns=-Item, decimals=2) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  ) |> 
  gt::opt_vertical_padding(scale = 0.7) |>
  gt::opt_horizontal_padding(scale = 0.5) |>
  # gt::tab_options(table.width = gt::pct(100)) |> 
  gt::cols_width(Label ~ gt::pct(30)) |>
  gt::gtsave("table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal

<object type="text/html" data="table1.html" width="120%" height="1000"></object>

@@

### Graph

```{r}
#| fig-width: 9
#| fig-height: 8
#| warning: false

graph <- convert2tidygraph(ega3)

replace_lowernames <- function(names, lower) {
  rownames(lower) <- lower$ID
  sprintf("%02d", as.numeric(lower[names, "Item"]))
}
replace_highernames <- function(names) {
  x <- as.numeric(str_remove(names, "L"))  
  paste0("C", sprintf("%02d", x))
}

# Arrange lower nodes in circle
lower_nodes <- graph$nodes |> 
  filter(level == "Lower") |> 
  mutate(name = fct_relevel(name, as.character(lower$ID)),
         ID = name) |> 
  arrange(name)  
lower_edges <- graph$edges |> 
  filter(from %in% lower_nodes$name & to %in% lower_nodes$name)
lower_layout <- tidygraph::tbl_graph(lower_nodes, edges=lower_edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'circle')
rownames(lower_layout) <- lower_nodes$name

# Arrange higher nodes in circle
higher_nodes <- graph$nodes |> 
  filter(level == "Higher") |> 
  mutate(ID = name,
         name = replace_highernames(name),
         name = fct_relevel(name, names(select(higher, -Item, -Cluster,-Max,-Label)))) |>
  arrange(name)
higher_edges <- graph$edges |> 
  filter(from %in% higher_nodes$name & to %in% higher_nodes$name)
higher_layout <- tidygraph::tbl_graph(higher_nodes, edges=higher_edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'circle')
rownames(higher_layout) <- higher_nodes$ID

# Put circles together
layout <- tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'linear', circular = TRUE)
layout[layout$level == "Lower", "x"] <- lower_layout[layout[layout$level == "Lower", "name"], "x"]
layout[layout$level == "Lower", "y"] <- lower_layout[layout[layout$level == "Lower", "name"], "y"]
layout[layout$level == "Higher", "x"] <- higher_layout[layout[layout$level == "Higher", "name"], "x"] * 0.5
layout[layout$level == "Higher", "y"] <- higher_layout[layout[layout$level == "Higher", "name"], "y"] * 0.5
layout[layout$level == "Lower", "name"] <- replace_lowernames(layout[layout$level == "Lower", "name"], lower)
layout[layout$level == "Higher", "name"] <- replace_highernames(layout[layout$level == "Higher", "name"])

# layout$dimmension_label <- layout$dimension
# layout[layout$level == "Higher", "dimmension_label"] <- NA

# layout[layout$level == "Higher", "dimension"] <- layout[layout$level == "Higher", "dimension"]

ggraph(layout) +
  geom_edge_link(aes(edge_alpha=as.numeric(type == "virtual"), edge_width = abs(link)), edge_width=0.2, color="grey") +
  geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real"))) +
  geom_node_point(aes(color=dimension, shape=level), size=12) +
  geom_node_text(aes(label=name), fontface="bold") +
  # geom_node_text(aes(label = dimmension_label, angle = node_angle(x, y), hjust = 'outward')) +
  scale_edge_alpha(range = c(0, 0.9), guide="none") +
  scale_edge_width(range = c(0.2, 3), guide="none") +
  scale_edge_colour_gradientn(colors=c("#E53935", "#E53935", "white", "#43A047", "#43A047"), 
                              values=c(-1, -0.5, 0, 0.5, 1), guide="none") +
  scale_shape_manual(values=c("Higher"="square", "Lower"="circle"), guide="none") +
  scale_color_manual(values=c(
    "H1"="#90CAF9", "H2"="#C5E1A5", "H3"="#EF9A9A", 
    "L1"="#CE93D8", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
    "L4"="#F3F29D", "L6"="#E6EE9C", "L15"="#D6E8A1", "L8"="#C5E1A5", "L10"="#B5DCA6", "L5"="#A5D6A7", "L2"="#93D1B6",
    "L17"="#CE93D8", "L14"="#F48FB1", "L12"="#EF9A9A", "L16"="#FFAB91", "L11"="#FFCC80", "L7"="#FFE082"),
                     breaks=c("H1", "H2", "H3")) +
  theme_void() +
  labs(color="Metaclusters")
```

### Model Comparison

# EGAnet::EGM(items[, 1:60])
EGAnet::EGM.compare(items, model = "glasso", algorithm = "leiden")
rez <- EGAnet::network.compare(byfacet, bymodality, model = "glasso", seed=3)

plot(rez)
```

@@

```{r}
#| message: false

# Modelbased scores
scores <- EGAnet::net.scores(
  items[names(ega3$typicalGraph$lower_order$wc)],
  A=ega3$typicalGraph$lower_order$graph,
  wc=ega3$typicalGraph$lower_order$wc)$scores$std.scores |>
  as.data.frame()
names(scores) <- paste0("C", names(scores))
